---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tiktokrmd

<!-- badges: start -->
<!-- badges: end -->

Embed TikTok videos in R Markdown things!

## Installation

You can install the released version of tictokrmd from GitHub:

``` r
remotes::install_github("gadenbuie/tiktokrmd")
```

## How to TikTok in R Markdown

```{r}
con <- textConnection("h", open = "w", local = TRUE)
tools::Rd2HTML("man/tiktok.Rd", con)
close(con)
first_h2 <- which(grepl("<h2>", h))[1] + 1
ex_heading <- which(grepl("<h3>Examples</h3>", h))
ex_pre <- which(grepl("pre>", h))
ex_pre_start <- ex_pre[length(ex_pre) - 1]
ex_pre_end <- ex_pre[length(ex_pre)]

example <- paste(h[(ex_pre_start + 1):(ex_pre_end - 1)], collapse = "\n")
example <- gsub("&lt;", "<", example)
example <- gsub("&gt;", ">", example)
example <- paste0("```{r echo=TRUE, eval=-6:-7}\nlibrary(tiktokrmd)\n\n", example, "\n```")

tmpfile <- tempfile(fileext = ".Rmd")
writeLines(example, tmpfile)

documentation <- h[first_h2:(ex_heading - 1)]
```

### Example

```{r child=tmpfile}
```

### &#x26A0;&#xFE0F; Previewing Locally &#x26A0;&#xFE0F;

TikTok's embedding script only works when the page with the embedded video is being served. For some reason, it doesn't seem to work when viewing a local file.

The easiest way around this is to use 
the **Infinite Moon Reader** addin (or `inf_mr()`) 
from [xaringan](https://github.com/yihui/xaringan) 
to render your R Markdown document. 
If you're working on a blog post, 
`blogdown::serve_site()` probably works fine.
In all cases, 
you'll still need to preview the rendered page in an external browser,
like FireFox, Chrome, or Safari.

```{r results="asis"}
cat("```{=html}", documentation, "```", sep = "\n")
```

```{r}
unlink(tmpfile)
```

